Placeholder title: Formal methods in constraint-based learning

### 2024-01-09 ITP draft/draft_lipics.tex
gitignore for latex + comment

A DL itself consists of syntax - the logical language used to express properties - and semantics - the "translation" from the syntax to a loss function. A general typed syntax and semantics for expressing different popular DLs that we use as a reference point is Logic of Differentiable Logics (LDL) CITE. The syntax of LDL is a typed first order logic language with addition of lambdas however in this paper we will consider its propositional fragment which can be seen in Figure \ref{fig:syntax}. Importantly the type system includes the existance of vectors, vector indicies and real numbers.

@@

>>>>

A DL itself consists of syntax - the logical language used to express properties - and semantics - the ``translation'' from the syntax to a loss function. A general typed syntax and semantics for expressing different popular DLs that we use as a reference point is Logic of Differentiable Logics (LDL) CITE. The syntax of LDL is a typed first order logic language with addition of lambdas however in this paper we will consider its propositional fragment which can be seen in Figure \ref{fig:syntax}. Importantly the type system includes the existance of vectors, vector indicies and real numbers.

@@

\natalia{I'm not sure if I should be using paragraphs or subsections or what in this style? I'd normally use a paragraph for contributions but they seemed to be numbered by default}
